Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-13 articles/cycle/alps-cycle.tex
Draft discussion of glacial cycle dynamics.

    \begin{itemize}
    \item Rapid variations of total ice volume (Fig.~\ref{fig:lgmvel}b).
    \item Two major glaciations during MIS 4 and 2 (Fig.~\ref{fig:lgmvel}b).
    \item Some glaciers advance many times (Fig.~\ref{fig:profiles}).
    \end{itemize}

>>>>

    As previously mentioned (Sect.~\ref{sec:timeseries}), independently of the
    palaeo-temperature (GRIP, EPICA, or MD01-2444) and palaeo-precipitation
    (with or without corrections) applied, all simulations presented here
    result in a high time variability in the total modelled ice volume
    (Fig.~\ref{fig:timeseries}). Unsurprisingly, this result is confirmed by
    the 1-km resolution run, using the optimal EPICA palaeo-temperature record
    (Sect.~\ref{sec:paltemp}) and conservatively includes palaeo-precipitation
    reductions (Sect.~\ref{sec:palprec}), which also results in strong total
    ice volume variability throughout the last glacial cycle
    (Fig.~\ref{fig:lgmvel}b).

    Two major glaciations occur during MIS~4 and 2 (Fig.~\ref{fig:lgmvel}b).
    However, several minor glaciations occur during MIS~5 and 3, as well as a
    minor late-glacial readvance at the onset of MIS~1
    (Fig.~\ref{fig:lgmvel}b). These episodes are the result of synchronous
    advances several Alpine glaciers well into the major valleys and sometimes
    even onto the foreland (Fig.~\ref{fig:profiles}), Supplementary animation).

    For instance the Rhine Glacier (Fig.~\ref{fig:profiles}a) reaches a lenght
    exceeding 130\,km, roughly corresponding to location of the last major
    Alpine reliefs and the beginning of the foothills, 6~times during the
    simulation, sometimes retreating almost to its present day frontal position
    (Fig.~\ref{fig:profiles}b). The Rhone Glacier, fed by several high-altitude
    accumulation areas, advanced 8\,times onto the location of modern Lake
    Geneva (Fig.~\ref{fig:profiles}c, d). The Ivrea Glacier, characterised by
    a very steep catchment, and mutliple tributaries, show even a higher
    variability and reaches close to its maximum position 6\,times throughout
    the simulation. Finally, the Isère Glacier, with its complex system of
    confluences and diffluences, needs longer time to build up and reaches the
    foreland only twice during the major glaciations of MIS~4 and 2.

    Despite the low temperature variability of the palaeo-climate forcing, and
    reduced precipitation dampening glacier response, our simulation depict
    the Alpine ice complex as highly dynamic, with dynamic of individual
    glaciers controlled by variations in subglacial topography and catchment
    geometry.
